---
title: "Explore DSB"
author: "Otto Perdeck"
date: "Friday, December 18, 2015"
output: html_document
---

Exploring the characteristics of the train data and the mock-up submission datasets that
are generated without respect to the images.

```{r}
library(tidyr)
library(data.table)
library(ggplot2)
library(dplyr)

train_ori <- fread('data/train.csv') 
train <- train_ori %>% gather(Phase, Volume, -Id)
summary(train_ori)
```

Cumulative Systole and Diastole distributions in the train dataset:

```{r, echo=FALSE}
qplot(Volume, data=train, stat = "ecdf", geom = "step", colour=Phase)

qplot(Phase, Volume, data=train, geom="boxplot", fill=Phase)+coord_flip()
```

Now, generate mock scores and analyze these.

See 
https://github.com/udibr/DSB2/blob/master/optimal.ipynb

```{r}
subm <- fread('analysis/submission.csv')[1:2,]
ds <- data.frame(Diastole = as.vector(t(subm[1,2:ncol(subm),with=F])),
                 Systole  = as.vector(t(subm[2,2:ncol(subm),with=F]))) 
ds$P <- 1:nrow(ds)
summary(ds)
```

Distribution of the generated data:

```{r, echo=FALSE}
ds_gathered <- gather(ds,Phase,Density,-P)
ds_gathered$Phase <- factor(ds_gathered$Phase, levels=levels(train$Phase))
ggplot(data=ds_gathered, aes(x=P, y=Density, colour=Phase))+geom_line()
```

```{r}
med_Diastole <- (ds %>% mutate(d = abs(0.5 - Diastole)) %>% arrange(d))$P[1]
med_Systole <- (ds %>% mutate(d = abs(0.5 - Systole)) %>% arrange(d))$P[1]

cat("Diastole median in generated data:",med_Diastole,"in train data",median(train_ori$Diastole),fill=T)
cat("Systole median in generated data:",med_Systole,"in train data",median(train_ori$Systole),fill=T)
```

Emulate the Python script in R. Result is the same as from the Python script. To generate different
curves, perhaps we just move the data from train_ori by a delta to the median? This assumes a similar
distribution.

```{r}
NPROBS <- 600
TESTIDS <- 501:700
doHist <- function(data) {
  h <- rep(0, NPROBS)
  for (j in (1+as.integer(ceiling(data)))) {
    h[j:NPROBS] <- h[j:NPROBS]+1
  }
  h <- h / length(data)
}
hSystole <- doHist(train_ori$Systole)
hDiastole <- doHist(train_ori$Diastole)
subm <- matrix(nrow = 2*length(TESTIDS), ncol = NPROBS)
for (i in 1:length(TESTIDS)) {
  Id <- TESTIDS[i]
  subm[2*i-1,] <- hDiastole
  subm[2*i,]   <- hSystole
}
subm <- data.frame(Id = as.vector(sapply(TESTIDS,function(n){paste(n,c('Diastole','Systole'),sep="_")})), subm)
names(subm) <- c('Id', paste("P",0:(NPROBS-1),sep=""))

# verify...
subm_py <- fread('analysis/submission.csv', data.table=F)
print(all(subm_py == subm))

```

Distribution of the generated data once again (from R this time):

```{r, echo=FALSE}
ds_plot <- gather(subm[1:2,],Volume,Density,-Id)
ds_plot$Volume <- as.integer(gsub("P(.*)","\\1",ds_plot$Volume))
ds_plot$Id <- factor(gsub(".*_(.*)","\\1",ds_plot$Id), levels=levels(train$Phase))
ggplot(data=ds_plot, aes(x=Volume, y=Density, colour=Id))+geom_line()
```
